Scale Space Edge Detection

### 2018-03-06 paper.tex
damn this appendix is long

Now that we have computed the spatial derivatives of the scale space representation of the image, we can check if we fulfill the conditions in (\ref{eq:c1}). 
The next step is to then calculate the edge strength derivatives neccessary to fulfill the conditions of (\ref{eq:c2}).
The code block below shows the computations for the edge strength based on the gradient magnitued and its derivatives.

@@

\lstinputlisting[caption={edge\_detect.jl},label=edge_detect]{edge_detect.jl}

>>>>

Now that we have computed the spatial derivatives of the scale space representation of the image, we can check if we fulfill the conditions in (\ref{eq:c1}). 
The next step is to then calculate the edge strength derivatives neccessary to fulfill the conditions of (\ref{eq:c2}).
The code block below shows the computations for the edge strength based on the gradient magnitude and its derivatives.

@@

\lstinputlisting[caption={edge\_detect.jl},label=edge_detect,frame=none]{edge_detect.jl}
